Whats reported in the news?

### 2018-03-13 paper/docs/04_Modelresults_50.Rmd
combine with polls

```{r}
topics <- matrix(c(1, "SPD", 2, "B90/ Die Grüne & DIE LINKE", 3, "Mix: Akhanli, Guttenberg, Bayern", 4, "Great Coalition debates", 5, "Diesel scandal", 6, "H.Kohl", 7, "Federal Election results", 8, "Europa, Macron, Schäuble", 9, "Mix: political trends, twitter", 10, "Merkel vs. Schulz", 11, "politics & democracy in GER", 12, "Deportation of criminal Refugees", 13, "A.Merkel", 14, "Text processing fail", 15, "Israel, antisemitism, D.Trump", 16, "Mix: political talkshows, Refugees", 17, "Intra-party vote (SPD) about the coalition w CDU/CSU", 18, "Election in Niedersachsen", 19, "R.Lammert", 20, "AfD, Right-wing extremist tendencies", 21, "German armed forces, v.d.Leyen", 22, "SPD, stuffing debates", 23, "CSU, Söder vs. Seehover, refugee cap", 24, "Bundespräsident F.-W.Steinmeier", 25, "Election polls", 26, "Reelections vs. Great Coalition after Jamaica failure", 27, "Jamaica caolition talks", 28, "G20 in Hamburg", 29, "Federal Constitutional Court, Ministry of the Interior", 30, "F.Petri, AfD", 31, "D.Trump, Russia", 32, "Gauland, Weidel, AfD", 33, "German armed forces, Mali", 34, "Mix: Children, Education, Women", 35, "Left- rightwing Terror, police reports", 36, "Mix: people, Germany, democracy", 37, "AfD in parliament", 38, "EU policies", 39, "Mix: Terror attacks", 40, "Mix: Metoo, SPD", 41, "Terror attack Berlin (Amri)", 42, "Refugee family reunion", 43, "Mix: studies", 44, "Federal Constitutional Court (NSU, Franco, Terror)", 45, "Mix: minister of the interior, environment", 46, "CDU, Spahn", 47, "Church", 48, "public (budget) statistics, Education/ Healthcare/ Digital policies", 49, "Turkey", 50, "Höcke, Holocaust"), ncol=2, byrow=T)

@@

# ggsave(plot = p1, filename = "../figs/estimates.png", device = "png",width = 10, height = 7,
# dpi = 600)
```

@@

```{r}
sentDF %>% filter(document == unique(sentDF$document)[1]) %>%
  select(title, word, value, site) %>%
  htmlTable::htmlTable(align = "l")
```

@@

$$
\text{Weighted}_d = \frac{|\text{positive polarity score}_d| - |\text{negative polarity score}_d|}{\text{Total Words}_d}
$$

```{r}
sentDF.values <- sentDF %>%
  select(document, word, value, 
         negative, positive,
         negative_d, positive_d) %>%
  group_by(document) %>%

@@

  # generate week
  mutate(week = week(date),
         month = as.character(month)) %>%
  mutate(week = paste(month,week, sep = "-"))
```

#### 2.2.5. Plot Sentiment Score

The following figure shows the results of the analysis for each topic on a monthly basis, aggregated on all newspaper. Some conclusions can be drawn from this illustration. First of all, it is clear that topics concerning the AfD (20, 30, 32, 37) are discussed in a negative way over the entire period, with an exepction for topic 30, dealing with Frauk Petry and the AfD. The topic that is discussed most negatively is that of the right-wing extremist tendencies within the AfD. Another striking result is that the sentiment score of topics topics that deal with the SPD alone (1, 22) is diminishing in the course of time. The topic, which contains the CDU in isolation (46), is rather zigzagging, with a high peak in November 2017 and a low peak in January 2018, but there is only one observation this month, which is an article about Peter Tauber's illness.

@@

##### By Month & Topic
```{r fig.height=10, fig.width=12}
p <- sentDF.values %>%
  group_by(month, topic_name, topic) %>%
  summarise(sentiment = mean(sentiment, na.rm=T),
            sentiment_d = mean(sentiment_d, na.rm=T),
            obs = n()) %>%
  ungroup()

p1 <- ggplot(p, 
       aes(month, sentiment, 
           group = topic_name,
           label = obs)) +
  facet_wrap(~topic_name, nrow = 3) +
  geom_col(fill = col[1], alpha = 0.7) +
 geom_line(color = col[2], size = 1) +
  geom_text() +
  geom_hline(yintercept = 0, linetype = 2,
             color = "black") +
  labs(x="", y="",
       title = "Monthly Sentiment Score") +
  theme(axis.text.y = element_text(size=8),
        axis.text.x = element_text(angle = 90, size = 6))

@@

```{r fig.height=5, fig.width=10}
p <- sentDF.values %>%
  group_by(site, topic_name, topic) %>%
  summarise(sentiment = mean(sentiment, na.rm=T),
            sentiment_d = mean(sentiment_d, na.rm=T),
            obs = n())

p1 <- ggplot(p, 
       aes(reorder(topic_name, topic), 
           sentiment, label = obs)) +
  geom_col(fill=col[2], alpha = 0.7) +
  geom_text(size = 2.5) +
  geom_hline(yintercept = 0, linetype = 2,
             color = "black") +
  coord_flip() +
  facet_wrap(~site, ncol = 7) +
  labs(x="", y="",
       title = "Sentiment Score") +
  theme(axis.text.y = element_text(size=8),
        axis.text.x = element_text(angle = 90))

@@

radar %>%
  ggRadar(aes(color=site), 
          rescale = F,
          alpha = 0, legend.position = "right") +
  labs(title = "Sentiment score Jun 2017-March 2018") +
  guides(col = guide_legend(nrow = 1)) +
  theme(legend.position = "bottom")
```

@@

<!-- ### 5. Compare with polls -->

```{r eval=FALSE, include=FALSE}
load("../output/polls.Rda")

@@

<!-- Define Functions  -->

```{r eval=FALSE, include=FALSE}
calculate_month = function(month, year) {
  date <- ymd(paste(year, 1, 1, sep="-"))
  month(date) = month
  return(date)
}

normalize_data <- function(x) {
  y <- (x - min(x, na.rm = T)) / (max(x, na.rm = T) - min(x, na.rm = T))
  return(y)
}
```

<!-- Prepare Dataframes -->

```{r eval=FALSE, include=FALSE}
polls <- table_long %>%
  mutate(month=month(Datum),
         year = year(Datum),
         yearmonth = calculate_month(month,year),
         val_norm = normalize_data(value)) %>%
  group_by(yearmonth,party) %>%
  summarise(mean_val = mean(value, na.rm=T),
            mean_val_norm = mean(val_norm)) %>%
  ungroup() %>%
  filter(mean_val != "NaN") %>%
  select(party, yearmonth, mean_val_norm) %>%
  spread(party, mean_val_norm)
```

```{r eval=FALSE, include=FALSE}
sentDF.values %>%
  mutate(year = year(date),
         month = month(date),
         yearmonth = calculate_month(month,year),
         sentiment_norm = normalize_data(sentiment)) %>%
  group_by(yearmonth, topic_name, topic, site) %>%
  summarise(mean_sent = mean(sentiment, na.rm=T),
            mean_sent_norm = mean(sentiment_norm, na.rm = T)) %>%
  ungroup() %>%
  left_join(polls, by="yearmonth") -> p
```

<!-- Plot  -->

```{r eval=FALSE, include=FALSE}
for (i in unique(p$site)) {

  p1 <- p %>%
  filter(site == i) %>%
  ggplot(aes(yearmonth, mean_sent_norm,
               group = site)) +
  geom_point(show.legend = F, color = col[1]) + 
  geom_line(color = col[1]) +

  scale_y_continuous(limits = c(0,1)) +
  scale_x_date(breaks = date_breaks("1 month"), 
               labels = date_format("%b", tz = "CET")) +
  # AfD
  geom_point(aes(yearmonth, AfD), size= 0.5,
             color = "deepskyblue") +
  geom_line(aes(yearmonth, AfD), color = "deepskyblue") +

  # CDU/CSU
  geom_point(aes(yearmonth, Union), size= 0.5,
             color = "black") +
  geom_line(aes(yearmonth, Union),
             color = "black") +

  # SPD
  geom_point(aes(yearmonth, SPD), size= 0.5,
             color = "red") +
  geom_line(aes(yearmonth, SPD),
             color = "red") +

  # Grüne
  geom_point(aes(yearmonth, Grüne), size= 0.5,
             color = "limegreen") +
  geom_line(aes(yearmonth, Grüne),
             color = "limegreen") +

  # DIE LINKE
  geom_point(aes(yearmonth, Linke), size= 0.5,
             color = "deeppink") +
  geom_line(aes(yearmonth, Linke),
             color = "deeppink") +

  # 
  labs(x="", y="", title=paste(i)) +
    theme(axis.text = element_text(size = 6)) +
  facet_grid(topic_name ~.)

  ggsave(p1, file=paste0("../figs/polls_",i,".png"),
         width = 4, height = 10)

<!-- <img src="../figs/polls_Bild.de.png", width = "49%"> -->
<!-- <img src="../figs/polls_DIE WELT.png", width = "49%"> -->
<!-- <img src="../figs/polls_FOCUS ONLINE.png", width = "49%"> -->
<!-- <img src="../figs/polls_SPIEGEL ONLINE.png", width = "49%"> -->
<!-- <img src="../figs/polls_stern.de.png", width = "49%"> -->
<!-- <img src="../figs/polls_Tagesschau.de.png", width = "49%"> -->
<!-- <img src="../figs/polls_ZEIT ONLINE.png", width = "49%"> -->

>>>>

```{r}
topics <- matrix(c(1, "SPD", 2, "B90/ Die Grüne & DIE LINKE", 3, "Mix: Akhanli, Guttenberg, Bayern", 4, "Great Coalition debates", 5, "Diesel scandal", 6, "H.Kohl", 7, "Federal Election results", 8, "Europa, Macron, Schäuble", 9, "Mix: political trends, twitter", 10, "Merkel vs. Schulz", 11, "politics & democracy in GER", 12, "Deportation of criminal Refugees", 13, "A.Merkel", 14, "Text processing fail", 15, "Israel, antisemitism, D.Trump", 16, "Mix: political talkshows, Refugees", 17, "Votes within SPD", 18, "Election in Niedersachsen", 19, "R.Lammert", 20, "AfD, Right-wing extremist tendencies", 21, "German armed forces, v.d.Leyen", 22, "SPD, stuffing debates", 23, "CSU, Söder vs. Seehover, refugee cap", 24, "Bundespräsident F.-W.Steinmeier", 25, "Election polls", 26, "Jamaica failure", 27, "Jamaica Coalition debates", 28, "G20 in Hamburg", 29, "Federal Constitutional Court, Ministry of the Interior", 30, "F.Petri, AfD", 31, "D.Trump, Russia", 32, "Gauland, Weidel, AfD", 33, "German armed forces, Mali", 34, "Mix: Children, Education, Women", 35, "Left- rightwing Terror, police reports", 36, "Mix: people, Germany, democracy", 37, "AfD in parliament", 38, "EU policies", 39, "Mix: Terror attacks", 40, "Mix: Metoo, SPD", 41, "Terror attack Berlin (Amri)", 42, "Refugee family reunion", 43, "Mix: studies", 44, "Federal Constitutional Court (NSU, Franco, Terror)", 45, "Mix: minister of the interior, environment", 46, "CDU, J.Spahn, Tauber (Disease)", 47, "Church", 48, "public (budget) statistics, Education/ Healthcare/ Digital policies", 49, "Turkey", 50, "Höcke, Holocaust"), ncol=2, byrow=T)

@@

ggsave(plot = p1, filename = "../figs/estimates.png", device = "png",width = 10, height = 7,
dpi = 600)
```

@@

```{r}
sentDF %>% filter(document == unique(sentDF$document)[2]) %>%
  select(title, word, value, site) %>%
  htmlTable::htmlTable(align = "l")
```

@@

$$
\text{Weighted}_d = \frac{|\text{positive polarity score}_d| - |\text{negative polarity score}_d|}{\text{Total Words}_d}
$$
```{r}
sentDF.values <- sentDF %>%
  select(document, word, value, 
         negative, positive,
         negative_d, positive_d) %>%
  group_by(document) %>%

@@

  # generate month & week
  mutate(week = week(date),
         month = month(date),
         year = year(date),
         yearmonth = calculate_month(month,year),
         yearweek = calculate_week(week, year)) 
```

#### 2.2.5. Plot Sentiment Score
```{r}
btw.2 %>% 
  mutate(yearmonth = calculate_month(month(date), year(date))) %>%
  group_by(yearmonth) %>%
  summarise(total_obs = n()) -> tally_month

btw.2 %>%
  group_by(site) %>%
  summarise(total_obs = n()) -> tally_site

btw.2 %>% 
  mutate(yearmonth = calculate_month(month(date),year(date))) %>%
  group_by(yearmonth, site) %>%
  summarise(total_obs = n()) -> tally_month_site
```

The following figure shows the results of the analysis for each topic on a monthly basis, aggregated on all newspaper. Each sentiment value is weighted by the relative share of the topic in the overall reporting of that month.

$$
\text{w} = \frac{\text{# of obs per month & topic}}{\text{# of obs per month}}
$$

$$
\text{weighted sentiment} = \text{sentiment} * \text{w}
$$

Some conclusions can be drawn from this illustration. First of all, it is clear that topics concerning the AfD (20, 30, 32, 37) are discussed in a negative way over the entire period, with an exepction for topic 30, dealing with Frauk Petry and the AfD. The topic that is discussed most negatively is that of the right-wing extremist tendencies within the AfD. Another striking result is that the sentiment score of topics topics that deal with the SPD alone (1, 22) is diminishing in the course of time. The topic, which contains the CDU in isolation (46), is rather zigzagging, with a high peak in November 2017 and a low peak in January 2018, but there is only one observation this month, which is an article about Peter Tauber's illness.

@@

##### By Month & Topic
```{r fig.height=12, fig.width=10}
p <- sentDF.values %>%
  group_by(yearmonth, topic_name, topic) %>%
  summarise(sentiment = mean(sentiment, na.rm=T),
            obs = n()) %>%
  left_join(., tally_month, by = "yearmonth") %>%
  mutate(w = obs / total_obs,
         sentiment_w = sentiment * w)

p1 <- ggplot(p, 
       aes(yearmonth, sentiment, 
           group = topic_name,
           label = obs)) +
  facet_wrap(~topic_name, nrow = 3) +
  geom_col(fill = col[1], alpha = 0.7) +
 geom_line(color = col[2], size = 0.8) +
  #geom_text() +
  geom_hline(yintercept = 0, linetype = 2,
             color = "black") +
  labs(x="", y="",
       title = "Monthly Sentiment Score",
       subtitle = "unweighted") +
  theme(axis.text.y = element_text(size=8),
        axis.text.x = element_text(size = 10))

p2 <- ggplot(p, 
       aes(yearmonth, sentiment_w, 
           group = topic_name,
           label = obs)) +
  facet_wrap(~topic_name, nrow = 3) +
  geom_col(fill = col[2], alpha = 0.7) +
 geom_line(color = col[1], size = 0.8) +
  #geom_text() +
  geom_hline(yintercept = 0, linetype = 2,
             color = "black") +
  labs(x="", y="",
       title = "",
       subtitle = "weighted") +
  theme(axis.text.y = element_text(size=8),
        axis.text.x = element_text(size = 10))

p1 + p2 + plot_layout(ncol = 1)
```

@@

The following figure shows the results of the analysis for each topic and each newspaper, aggregated over time. Each sentiment value is weighted by the relative share of the topic in the overall political news coverage of that online newspaper.

$$
\text{w} = \frac{\text{# of obs per newspaper & topic}}{\text{# of obs per newspaper}}
$$

$$
\text{weighted sentiment} = \text{sentiment} * \text{w}
$$

```{r fig.height=12, fig.width=10}
p <- sentDF.values %>%
  group_by(site, topic_name, topic) %>%
  summarise(sentiment = mean(sentiment, na.rm=T),
            obs = n()) %>%
  left_join(., tally_site, by = "site") %>%
  mutate(w = obs/total_obs,
         sentiment_w = sentiment * w)

p1 <- ggplot(p, 
       aes(reorder(topic_name, topic), 
           sentiment, 
           group = site,
           label = obs)) +
  geom_col(fill=col[2], alpha = 0.7) +
  #geom_line(color = col[1], size = 0.8) +
  #geom_text(size = 2.5) +
  geom_hline(yintercept = 0, linetype = 2,
             color = "black") +
  coord_flip() +
  facet_wrap(~site, ncol = 7) +
  labs(x="", y="",
       title = "Sentiment Score",
       subtitle = "unweighted") +
  theme(axis.text.y = element_text(size = 10),
        axis.text.x = element_text(size=6))

p2 <- ggplot(p, 
       aes(reorder(topic_name, topic), 
           sentiment_w, 
           group = site,
           label = obs)) +
  geom_col(fill=col[1], alpha = 0.7) +
  #geom_line(color = col[2], size = 0.8) +
  #geom_text(size = 2.5) +
  geom_hline(yintercept = 0, linetype = 2,
             color = "black") +
  coord_flip() +
  facet_wrap(~site, ncol = 7) +
  labs(x="", y="",
       title = "",
       subtitle = "weighted") +
  theme(axis.text.y = element_text(size = 10),
        axis.text.x = element_text(size=6))

p1 + p2 + plot_layout(ncol = 1)
```

@@

radar %>%
  ggRadar(aes(color=site), 
          rescale = F,
          alpha = 0, legend.position = "right") +
  labs(title = "Sentiment score Jun 2017-March 2018",
       subtitle = "unweighted") +
  guides(col = guide_legend(nrow = 1)) +
  theme(legend.position = "bottom")
```

```{r fig.height=10, fig.width=10}
sentDF.values %>%
  group_by(site, topic_name) %>%
  summarise(sentiment = mean(sentiment, na.rm=T),
            obs = n()) %>%
  left_join(., tally_site, by = "site") %>%
  mutate(w = obs/total_obs,
         sentiment_w = sentiment * w) %>%
  select(site, topic_name, sentiment_w) %>%
  spread(key=topic_name, value=sentiment_w) -> radar

radar %>%
  ggRadar(aes(color=site), 
          rescale = F,
          alpha = 0, legend.position = "right") +
  labs(title = "Sentiment score Jun 2017-March 2018",
       subtitle = "weighted") +
  guides(col = guide_legend(nrow = 1)) +
  theme(legend.position = "bottom")
```

@@

## 3. Compare with polls

```{r}
load("../output/polls.Rda")

@@

Prepare Dataframes

```{r}
polls <- table_long %>%
  mutate(month=month(Datum),
         year = year(Datum),
         yearmonth = calculate_month(month,year)) %>%
  group_by(yearmonth,party) %>%
  summarise(mean_val = mean(value, na.rm=T)) %>%
  ungroup() %>%
  filter(mean_val != "NaN") %>%
  select(party, yearmonth, mean_val) %>%
  spread(party, mean_val)
```

#### CDU

```{r fig.height=12, fig.width=10}
polls.red <- polls %>%
  filter(yearmonth > as.Date("2017-05-01")) %>%
  mutate(Union = normalize_data(Union))

topics.red <- sentDF.values %>%
  filter(grepl(paste("CDU","CSU","coalition", sep="|"), 
               topic_name, ignore.case = T))

### plot by time
p <-topics.red %>%
  group_by(yearmonth, topic_name, topic) %>%
  summarise(sentiment = mean(sentiment, na.rm=T),
            obs = n()) %>%
  ungroup() %>%
  left_join(., tally_month, by="yearmonth") %>%
  mutate(w = obs / total_obs,
         sentiment_w = sentiment * w,
         sentiment_n = normalize_data(sentiment_w))

### Plot 1  
p1 <- ggplot() +
  geom_col(data=p, aes(yearmonth, sentiment_n, 
             group = topic_name,
             fill = topic_name),
           position = "dodge", 
           alpha = 0.8) +
  scale_fill_manual(values = col) +
  guides(fill = guide_legend(ncol=3)) +

  # Add poll line
  geom_line(data = polls.red, 
            aes(yearmonth, Union),
            color = "black",
            size = 1) +
  labs(y="", x="", fill="",
       title = "Sentiment & Poll Values",
       subtitle = "Both scores are normalized") +
  scale_x_date(breaks = date_breaks("1 month"), labels=date_format("%B", tz="CET")) +
  theme(legend.position = "bottom")

### plot by time and site
p <- topics.red %>%
  group_by(yearmonth, topic_name, topic, site) %>%
  summarise(sentiment = mean(sentiment, na.rm=T),
            obs = n()) %>%
  ungroup() %>%
  left_join(., tally_month_site, by=c("yearmonth","site")) %>%
  mutate(w = obs / total_obs,
         sentiment_w = sentiment * w,
         sentiment_n = normalize_data(sentiment_w))

### Plot 2
p2 <- ggplot() +
  geom_col(data = p,
           aes(yearmonth, sentiment_n, 
             group = topic_name,
             fill = topic_name),
           alpha = 0.8,
           position = "dodge") +
  scale_fill_manual(values = col) +
  facet_wrap(~site, ncol = 2) +
   # Add poll line
  geom_line(data = polls.red, 
            aes(yearmonth, Union),
            color = "black",
            size = 1) +
  labs(y="", x="", fill="") +
  scale_x_date(breaks = date_breaks("1 month"), labels=date_format("%B", tz="CET")) +
  theme(legend.position = "none",
        axis.text.x = element_text(angle = 90))

p1 + p2 + plot_layout(ncol = 1, heights = c(1,4))
```

#### SPD
```{r fig.height=12, fig.width=10}
polls.red <- polls %>%
  filter(yearmonth > as.Date("2017-05-01")) %>%
  mutate(SPD = normalize_data(SPD))

topics.red <- sentDF.values %>%
  filter(grepl(paste("SPD", sep="|"), topic_name, ignore.case = T))

### plot by time
p <-topics.red %>%
  group_by(yearmonth, topic_name, topic) %>%
  summarise(sentiment = mean(sentiment, na.rm=T),
            obs = n()) %>%
  ungroup() %>%
  left_join(., tally_month, by="yearmonth") %>%
  mutate(w = obs / total_obs,
         sentiment_w = sentiment * w,
         sentiment_n = normalize_data(sentiment_w))

### Plot 1  
p1 <- ggplot() +
  geom_col(data=p, aes(yearmonth, sentiment_n, 
             group = topic_name,
             fill = topic_name),
           position = "dodge", 
           alpha = 0.8) +
  scale_fill_manual(values = col) +
  guides(fill = guide_legend(ncol=3)) +

  # Add poll line
  geom_line(data = polls.red, 
            aes(yearmonth, SPD),
            color = "red",
            size = 1) +
  labs(y="", x="", fill="",
       title = "Sentiment & Poll Values",
       subtitle = "Both scores are normalized") +
  scale_x_date(breaks = date_breaks("1 month"), labels=date_format("%B", tz="CET")) +
  theme(legend.position = "bottom")

### plot by time and site
p <- topics.red %>%
  group_by(yearmonth, topic_name, topic, site) %>%
  summarise(sentiment = mean(sentiment, na.rm=T),
            obs = n()) %>%
  ungroup() %>%
  left_join(., tally_month_site, by=c("yearmonth","site")) %>%
  mutate(w = obs / total_obs,
         sentiment_w = sentiment * w,
         sentiment_n = normalize_data(sentiment_w))

### Plot 2
p2 <- ggplot() +
  geom_col(data = p,
           aes(yearmonth, sentiment_n, 
             group = topic_name,
             fill = topic_name),
           alpha = 0.8,
           position = "dodge") +
  scale_fill_manual(values = col) +
  facet_wrap(~site, ncol = 2) +
   # Add poll line
  geom_line(data = polls.red, 
            aes(yearmonth, SPD),
            color = "red",
            size = 1) +
  labs(y="", x="", fill="") +
  scale_x_date(breaks = date_breaks("1 month"), labels=date_format("%B", tz="CET")) +
  theme(legend.position = "none",
        axis.text.x = element_text(angle = 90))

p1 + p2 + plot_layout(ncol = 1, heights = c(1,4))
```

#### FDP

```{r fig.height=12, fig.width=10}
polls.red <- polls %>%
  filter(yearmonth > as.Date("2017-05-01")) %>%
  mutate(FDP = normalize_data(FDP))

topics.red <- sentDF.values %>%
  filter(grepl(paste("Jamaica", sep="|"), 
               topic_name, ignore.case = T))

### plot by time
p <-topics.red %>%
  group_by(yearmonth, topic_name, topic) %>%
  summarise(sentiment = mean(sentiment, na.rm=T),
            obs = n()) %>%
  ungroup() %>%
  left_join(., tally_month, by="yearmonth") %>%
  mutate(w = obs / total_obs,
         sentiment_w = sentiment * w,
         sentiment_n = normalize_data(sentiment_w))

### Plot 1  
p1 <- ggplot() +
  geom_col(data=p, aes(yearmonth, sentiment_n, 
             group = topic_name,
             fill = topic_name),
           position = "dodge", 
           alpha = 0.8) +
  scale_fill_manual(values = col) +
  guides(fill = guide_legend(ncol=3)) +

  # Add poll line (FDP)
  geom_line(data = polls.red, 
            aes(yearmonth, FDP),
            color = col[4],
            size = 1) +
  labs(y="", x="", fill="",
       title = "Sentiment & Poll Values",
       subtitle = "Both scores are normalized") +
  scale_x_date(breaks = date_breaks("1 month"), labels=date_format("%B", tz="CET")) +
  theme(legend.position = "bottom")

### plot by time and site
p <- topics.red %>%
  group_by(yearmonth, topic_name, topic, site) %>%
  summarise(sentiment = mean(sentiment, na.rm=T),
            obs = n()) %>%
  ungroup() %>%
  left_join(., tally_month_site, by=c("yearmonth","site")) %>%
  mutate(w = obs / total_obs,
         sentiment_w = sentiment * w,
         sentiment_n = normalize_data(sentiment_w))

### Plot 2
p2 <- ggplot() +
  geom_col(data = p,
           aes(yearmonth, sentiment_n, 
             group = topic_name,
             fill = topic_name),
           alpha = 0.8,
           position = "dodge") +
  scale_fill_manual(values = col) +
  facet_wrap(~site, ncol = 2) +
    # Add poll line (FDP)
  geom_line(data = polls.red, 
            aes(yearmonth, FDP),
            color = col[4],
            size = 1) +
  labs(y="", x="", fill="") +
  scale_x_date(breaks = date_breaks("1 month"), labels=date_format("%B", tz="CET")) +
  theme(legend.position = "none",
        axis.text.x = element_text(angle = 90))

p1 + p2 + plot_layout(ncol = 1, heights = c(1,4))
```

#### B90 / Die Grüne

```{r fig.height=12, fig.width=10}
polls.red <- polls %>%
  filter(yearmonth > as.Date("2017-05-01")) %>%
  mutate(Grüne = normalize_data(Grüne))

topics.red <- sentDF.values %>%
  filter(grepl(paste("Jamaica","Grüne", sep="|"), 
               topic_name, ignore.case = T))

### plot by time
p <-topics.red %>%
  group_by(yearmonth, topic_name, topic) %>%
  summarise(sentiment = mean(sentiment, na.rm=T),
            obs = n()) %>%
  ungroup() %>%
  left_join(., tally_month, by="yearmonth") %>%
  mutate(w = obs / total_obs,
         sentiment_w = sentiment * w,
         sentiment_n = normalize_data(sentiment_w))

### Plot 1  
p1 <- ggplot() +
  geom_col(data=p, aes(yearmonth, sentiment_n, 
             group = topic_name,
             fill = topic_name),
           position = "dodge", 
           alpha = 0.8) +
  scale_fill_manual(values = col) +
  guides(fill = guide_legend(ncol=3)) +

    # Add poll line (Grüne)
  geom_line(data = polls.red, 
            aes(yearmonth, Grüne),
            color = "limegreen",
            size = 1) +
  labs(y="", x="", fill="",
       title = "Sentiment & Poll Values",
       subtitle = "Both scores are normalized") +
  scale_x_date(breaks = date_breaks("1 month"), labels=date_format("%B", tz="CET")) +
  theme(legend.position = "bottom")

### plot by time and site
p <- topics.red %>%
  group_by(yearmonth, topic_name, topic, site) %>%
  summarise(sentiment = mean(sentiment, na.rm=T),
            obs = n()) %>%
  ungroup() %>%
  left_join(., tally_month_site, by=c("yearmonth","site")) %>%
  mutate(w = obs / total_obs,
         sentiment_w = sentiment * w,
         sentiment_n = normalize_data(sentiment_w))

### Plot 2
p2 <- ggplot() +
  geom_col(data = p,
           aes(yearmonth, sentiment_n, 
             group = topic_name,
             fill = topic_name),
           alpha = 0.8,
           position = "dodge") +
  scale_fill_manual(values = col) +
  facet_wrap(~site, ncol = 2) +

    # Add poll line (Grüne)
  geom_line(data = polls.red, 
            aes(yearmonth, Grüne),
            color = "limegreen",
            size = 1) +
  labs(y="", x="", fill="") +
  scale_x_date(breaks = date_breaks("1 month"), labels=date_format("%B", tz="CET")) +
  theme(legend.position = "none",
        axis.text.x = element_text(angle = 90))

p1 + p2 + plot_layout(ncol = 1, heights = c(1,4))
```

#### AfD

```{r fig.height=12, fig.width=10}
polls.red <- polls %>%
  filter(yearmonth > as.Date("2017-05-01")) %>%
  mutate(AfD = normalize_data(AfD))

topics.red <- sentDF.values %>%
  filter(grepl(paste("AfD", sep="|"), 
               topic_name, ignore.case = T))

### plot by time
p <-topics.red %>%
  group_by(yearmonth, topic_name, topic) %>%
  summarise(sentiment = mean(sentiment, na.rm=T),
            obs = n()) %>%
  ungroup() %>%
  left_join(., tally_month, by="yearmonth") %>%
  mutate(w = obs / total_obs,
         sentiment_w = sentiment * w,
         sentiment_n = normalize_data(sentiment_w))

### Plot 1  
p1 <- ggplot() +
  geom_col(data=p, aes(yearmonth, sentiment_n, 
             group = topic_name,
             fill = topic_name),
           position = "dodge", 
           alpha = 0.8) +
  scale_fill_manual(values = col) +
  guides(fill = guide_legend(ncol=3)) +

    # Add poll line (AfD)
  geom_line(data = polls.red, 
            aes(yearmonth, AfD),
            color = "skyblue",
            size = 1) +
  labs(y="", x="", fill="",
       title = "Sentiment & Poll Values",
       subtitle = "Both scores are normalized") +
  scale_x_date(breaks = date_breaks("1 month"), labels=date_format("%B", tz="CET")) +
  theme(legend.position = "bottom")

### plot by time and site
p <- topics.red %>%
  group_by(yearmonth, topic_name, topic, site) %>%
  summarise(sentiment = mean(sentiment, na.rm=T),
            obs = n()) %>%
  ungroup() %>%
  left_join(., tally_month_site, by=c("yearmonth","site")) %>%
  mutate(w = obs / total_obs,
         sentiment_w = sentiment * w,
         sentiment_n = normalize_data(sentiment_w))

### Plot 2
p2 <- ggplot() +
  geom_col(data = p,
           aes(yearmonth, sentiment_n, 
             group = topic_name,
             fill = topic_name),
           alpha = 0.8,
           position = "dodge") +
  scale_fill_manual(values = col) +
  facet_wrap(~site, ncol = 2) +

    # Add poll line (AfD)
  geom_line(data = polls.red, 
            aes(yearmonth, AfD),
            color = "skyblue",
            size = 1) +
  labs(y="", x="", fill="") +
  scale_x_date(breaks = date_breaks("1 month"), labels=date_format("%B", tz="CET")) +
  theme(legend.position = "none",
        axis.text.x = element_text(angle = 90))

p1 + p2 + plot_layout(ncol = 1, heights = c(1,4))
```
